Numerical Investigation of Viscous Flow Instabilities in Heterogeneous Porous Media

### 2017-12-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

\title{ Numerical Investigation of Viscous Flow Instabilities in Heterogeneous Porous Media}%. Advantages and limitations of unstructured and adaptive meshes in 2D and 3D domains under different mobility scenarios.}

@@

\noindent respectively, where $\mu$, ${\bf K}$, $p$ and $\phi$ are viscosity, absolute permeability, pressure and porosity, respectively. ${\mathbf u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability. $\mathcal{S}$ is the source term associated with the Darcy and continuity equations. $S_{\alpha}$ represents the saturation of the $\alpha$-phase with mass conservation constraints of 
\begin{displaymath}
\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1, 
\end{displaymath}
where $\mathcal{N}_{p}$ denotes the number of phases.

>>>>

  \title{ Numerical Investigation of Viscous Flow Instabilities in Heterogeneous Porous Media}%. Advantages and limitations of unstructured and adaptive meshes in 2D and 3D domains under different mobility scenarios.}
  %% Tittle was too long and 'Advantages and limitations unstructured and adaptive meshes' would mean a full numerical analysis on these 2 issues ... we haven't fully studied flows in either  unstructured / structured or adaptive / fixed meshes ...

@@

\noindent respectively, where $\mu$, ${\bf K}$, $p$ and $\phi$ are viscosity, absolute permeability, pressure and porosity, respectively. ${\mathbf u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability. $\mathcal{S}$ is the source term associated with the Darcy and continuity equations. $S_{\alpha}$ represents the saturation of the $\alpha$-phase with mass conservation constraints of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
%\begin{displaymath}
%\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1, 
%\end{displaymath}
%where $\mathcal{N}_{p}$ denotes the number of phases.
